---
title       : Shining on International Airline travellers 
subtitle    : 
author      : Kay Dee
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : prettify      # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []   # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Description

We explore simple time series decomposition and forecasting. The chief features of the app

  * We use `dygraphs` package for interactive charting 
  * An example of time series decomposition using `loess`
  * Forecasting of time series using `Holt-Winters Filtering`

The app is running [shiny server](https://abysmon.shinyapps.io/AirPassenger/).
Sourcecode is on [github](https://github.com/abysmon/devDataProd/).

--- .class #id 

## What is it about

`AirPassengers` is contains monthly international airline passengers, in thousands, from 1949 to 1960. 

Summary
```{r, echo=FALSE,comment=NA, fig.width=6, fig.height=4,f}
summary(AirPassengers)
par(mar = c(4,4,1.5,1))
plot(AirPassengers, main = 'Monthly international airline passengers', col = 'gold2', lwd = 2, ylab = 'Passengers (Thousands)')
```


--- .class #id 

## What do we do

We split the dataset into seasonal component and the trend line

```{r, echo=FALSE,comment=NA, fig.width=13, fig.height=5}
ap.comp = stl(AirPassengers, s.window = 'periodic')

par(mfrow = c(1,3))
plot(ap.comp$time.series[,2], main = 'Trend line', col = 'cornflowerblue', lwd = 3, ylab = '')
plot(ap.comp$time.series[,1], main = 'Seasonal Component', col = 'coral', ylab = '')
plot(ap.comp$time.series[,3], main = 'Irregular Component', col = 'cyan4', ylab = '')
```

--- .class #id 

## What do we do (contd..)
Then we forecast it from upto 60 months ahead with two user controlled input
  *  Forecast ahead months
  *  Prediction bounds

**The predicted data and measured data are shown below**
```{r, echo=FALSE,comment=NA, fig.width=5, fig.height=4}
plot(forecast::hw(AirPassengers, 12), col ='turquoise3', lwd = 2)
```



